\LARGE \bf Artifical Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-16 paper.tex
Fixing language 7

The next section introduces the architecture as a whole, as well as the
knowledge model that we have developed for our robots. Then,
Section~\ref{sec:impl} details each of the main components of the
architecture, and highlights their significance for artificial
intelligence. Section~\ref{sec:expe} presents two studies that illustrate in a
practical way what can be currently achieved with our robots.
Section~\ref{sect|conclusion} finally restate our main contributions and discuss
the key challenges that human-robot interaction brings to artificial
intelligence.

@@

\subsection{\emph{Cleaning the table} study}

@@

\section{Discussion: When Artificial Intelligence Enables Human-Robot
Interaction}
\label{sect|conclusion}

This last section tries to clarify the ``takeaway'' message: what are the
challenges that human-robot interaction brings to artificial intelligence?  We
first restate the challenge of \emph{embodied cognition} in general and
summarise what we see as the main decisional issues that need to be tackled to
push forward human-robot interaction. Finally, we reflect on the importance of
knowledge handling in robotic architectures that deal with complex semantics and
put into perspective our choice of the RDF formalism.

@@

Robotics is traditionally regarded as the prototypical instance of
\emph{embodied} artificial intelligence, and this dimension is especially
prevalent in human-robot interaction, where agents have to share and collaborate
in a joint physical environment.

This leads to a tight coupling between the symbolic and the geometric realms:
while AI at its origins was mostly a matter of symbolic models, it has been
since recognised that not only the mind is not a purely abstract system,
disconnected from the physical world, but even more, cognition fundamentally
relies on its relation to the physical world (so-called \emph{embodied
cognition}). Varela~\cite{Varela1992} is one of the main discoverers of these
mechanisms, and coined the concept of \emph{enactivism} as the theoretical
framework that study the links between cognition, embodiment and actions.  This
has since been thoroughly studied in robotics and artificial intelligence
(Pfeifer and Bongard~\cite{pfeifer2007body} is one of the reference).

@@

\subsection{The Key Decisional Issues}

With this perspective on \emph{embodied cognition} in mind, it seems appropriate
to restate the key challenges brought by human-robot interaction to artificial
intelligence.

\subsubsection{The W-questions}

@@

\subsubsection{Putting the Humans into Equations}

@@

As thorougly presented in this article, we have built the decisional
capabilities of our robots around this idea of explicit knowledge manipulation.
We finally briefely comment on this design choice, our implementation based on RDF,
and the limitations that we perceive.

@@

One prototypical example of semantic disambiguation has been given in
\cite{Ros2010b} with the child game \emph{spygame}: two players are facing
each other with a set of random objects in-between, one player mentally choose
one object, and the other player has to guess the object by asking closed
questions like \emph{Is your object small or large?} Based on the knowledge it
has acquired, the robot is able to minimise the number of questions required to
find the object.

@@

The design choices and the results presented here are still preliminary.
While the general scheme we propose might be difficult to implement in
a general sense, we believe that it is a reasonable challenge to
implement it in the case of a personal robot assistant essentially
devoted to fetch-and-carry, as well as for interactive manipulation
tasks and associated activities.

@@

Another broader direction to head deals with \emph{contexts representation}.
Contexts are currently often limited to the current spatial and temporal
situation. Some models offer the possibility to jump in the past or to
switch to another agent's perspective, but in current approaches, selecting a
context always basically consists in retrieving a set of beliefs corresponding
to a situation, and temporarily replacing the current beliefs by those other
ones. This misses the fact that at a given moment, not one but many contexts
co-exist at different scales. We do not want to retrieve one monolithic set of
beliefs, but instead carefully craft a context from several \emph{atomic}
contexts. Techniques for representation of overlapping pools of knowledge
largely remain to be developed, as well as efficient algorithms to retrieve (or
discard) such context-related pools of knowledge. This is a challenge not only
for robotics, but more generally for artificial intelligence.

The ability to explicitly manage contexts and context switches would endow the
robot with a cognitive capability similar to what is known as
\emph{context-dependent memory} in cognitive psychology. This is also related
to Tulving's \emph{autonoetic consciousness}~\cite{Tulving1985a}: the ability
to reflect upon its own past or future experiences.

Much remain to be done to this regard, starting with a formal analysis of what
are the relevant contexts for our robots.

>>>>

The next section introduces the architecture as a whole, as well as the
knowledge model that we have developed for our robots. Then,
Section~\ref{sec:impl} details each of the main components of the architecture,
and highlights their significance for artificial intelligence.
Section~\ref{sec:expe} presents two studies that illustrate in a practical way
what can be currently achieved with our robots.  The
Sections~\ref{sect|discussion} and~\ref{sect|conclusion} finally restate our
main contributions and discuss the key challenges that human-robot interaction
brings to artificial intelligence.

@@

\subsection{\emph{Cleaning the table} Study}

@@

\section{Discussion: When Artificial Intelligence Enables Human-Robot
Interaction}
\label{sect|discussion}

The previous sections provide a perspective on a complete deliberative
architecture for social robots, including an implementation supported
``real-world'' experimental deployments. This section synthesises next what we
see as the main challenges that human-robot interaction brings to artificial
intelligence.  We discuss first how embodied cognition is a very real challenge
in human-robot interaction; we rephrase then the requirements of joint actions
in terms of five questions; we discuss the importance of building and
maintaining a multi-level model of the human; and we finally reflect on the
importance of explicit knowledge management in robotic architectures that deal
with human-level semantics and state in that respect the current limits of our
logic framework.

@@

Robotics is traditionally regarded as the prototypical instance of
\emph{embodied} artificial intelligence, and this dimension is especially
prevalent in human-robot interaction, where agents have to share and
collaborate in a joint physical environment.  This leads to a tight coupling
between the symbolic and the geometric realms: while AI at its origins was
mostly concerned with symbolic models, it has been since recognised that not
only the mind is not a purely abstract system, disconnected from the physical
world, but even more, cognition fundamentally relies on its relation to the
physical world (so-called \emph{embodied cognition}). Varela~\cite{Varela1992}
is one of the main discoverers of these mechanisms, and coined the concept of
\emph{enactivism} as the theoretical framework that study the links between
cognition, embodiment and actions.  This has since been thoroughly studied in
robotics and artificial intelligence (Pfeifer and
Bongard~\cite{pfeifer2007body} is one of the reference).

@@

\subsection{The W-questions of Joint Action}

@@

\subsection{Putting the Humans into Equations}

@@

As thoroughly presented in this article, we have built the decisional
capabilities of our robots around this idea of explicit knowledge manipulation.
We finally briefly comment on this design choice and the limitations that we
have observed.

@@

We have studied a prototypical example of semantic disambiguation in
\cite{Ros2010b} with the children's ``spygame'': two players are facing
each other with a set of random objects in-between, one player mentally choose
one object, and the other player has to guess the object by asking closed
questions like \emph{Is your object small or large?} Based on the knowledge it
has acquired, the robot is able to minimise the number of questions required to
find the object.

@@

The design choices and the results presented here are still preliminary.
While the general scheme we propose might be difficult to implement in
a general sense, we believe that it is a reasonable challenge to
implement it in the case of a personal robot assistant essentially
devoted interactive manipulation
tasks and associated activities.

@@

Another direction to head to deals with \emph{contexts representation}.
Contexts are currently often limited to the current spatial and temporal
situation. Some models offer the possibility to jump in the past or to switch to
another agent's perspective, but in current approaches, selecting a context
always basically consists in retrieving a set of beliefs corresponding to a
situation, and temporarily replacing the current beliefs by those other ones.
This misses the fact that at a given moment, not one but many contexts co-exist
at different scales. We do not want to retrieve one monolithic set of beliefs,
but instead carefully craft a context from several \emph{atomic} contexts.
Techniques for representation of overlapping pools of knowledge largely remain
to be developed, as well as efficient algorithms to retrieve (or discard) such
context-related pools of knowledge. This is a challenge not only for robotics,
but more generally for artificial intelligence.  The ability to explicitly
manage contexts and context switches would endow the robot with a cognitive
capability similar to what is known as \emph{context-dependent memory} in
cognitive psychology. This is also related to Tulving's \emph{autonoetic
consciousness}~\cite{Tulving1985a}: the ability to reflect upon its own past or
future experiences.  Much remain to be done to this regard, starting with a
formal analysis of what are the relevant contexts for our robots.
